On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-10-17 Manuscript/manuscript.tex
fixed one typo

Figure~\ref{fig:VenueEffects} further illustrates the venue effect from 1999 to
2023 based on the full GLMM both with and without 2022.  The temporal patterns
of the two sets of effects look very similar, except that the positive effects
estimated with 2022 included have higher magnitude than those estimated without
2022, which compensates the negative effect of the 2022 with a large magnitude.
Both plots agree to some extent with the pattern of the boxplots in
Figure~\ref{fig:Boxplot}. The mismatch is due to the heat effect, since the nevue
effect only captures a smaller part of the variation than the heat effect as
evident from their standard deviations. The venue effect for 2022 is
lower than that for any other year, but may not be as extreme as one would
think considering the history of reaction times going back to 1999.

>>>>

Figure~\ref{fig:VenueEffects} further illustrates the venue effect from 1999 to
2023 based on the full GLMM both with and without 2022.  The temporal patterns
of the two sets of effects look very similar, except that the positive effects
estimated with 2022 included have higher magnitude than those estimated without
2022, which compensates the negative effect of the 2022 with a large magnitude.
Both plots agree to some extent with the pattern of the boxplots in
Figure~\ref{fig:Boxplot}. The mismatch is due to the heat effect, since the venue
effect only captures a smaller part of the variation than the heat effect as
evident from their standard deviations. The venue effect for 2022 is
lower than that for any other year, but may not be as extreme as one would
think considering the history of reaction times going back to 1999.
